Blocking-resistant communication\\through domain fronting

### 2014-08-01 docs/meek.tex
Just have to be similar enough.

So far we do not find any obvious traffic characteristics that can be useful to reliably distinguish meek
from other HTTPS traffic.
The long-lived connections and few common packet sizes are
potential targets for a more concerted attack.
The fundamental problem we face is essentially that of steganography,
the need to make our traffic fit some model of ``normal'' traffic.
The problem is inherently difficult,
because it is difficult to say just what normal traffic \emph{is}.
It depends on the network environment;
it also depends on the endpoint.
Google is likely to be different than Akamai,
and it is hard to characterize what normal use of a CDN is:
they provide access to ordinary web sites,
but also video streams and software updates,
and not all clients are browsers.
The difficulty is symmetric;
if finding the right model is difficult task for us,
it is also difficult for the censor.
We have seen that censors prefer to use easy classifiers when they exist.
By removing the easy ways, we increase the cost to the censor.

>>>>

So far we do not find any obvious traffic characteristics that can be useful to reliably distinguish meek
from other HTTPS traffic.
The long-lived connections and few common packet sizes are
potential targets for a more concerted attack.
The fundamental problem we face is essentially that of steganography,
the need to make our traffic fit some model of ``normal'' traffic.
The problem is inherently difficult,
because it is difficult to say just what normal traffic \emph{is}.
It depends on the network environment;
it also depends on the endpoint.
Google's traffic is likely to be different than Akamai's.

For the purposes of censorship circumvention,
one doesn't need to match exactly a ``typical'' traffic profile;
only not to deviate from it too much.
Circumvention traffic must only be difficult enough to distinguish,
that blocking requires a number of false positives unacceptable to the censor.
Even 1\% of Google traffic accidentally blocked may exceed the collateral damage tolerance of some censors.
Further, it is hard to characterize what normal use is, of, say, a CDN:
they provide access to ordinary web sites,
but also to video streams and software updates,
and not all clients are browsers.
The difficulty we face is symmetric;
if finding the right model is difficult task for us,
it is also difficult for the censor.
We have seen that censors prefer to use easy classifiers when they exist.
By removing the easy ways, we increase the cost to the censor.
